### 2017-10-19 paper/sections/6_results.tex
paper: draft 2 with partial reads
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% Does this implementation need to be described in the implementation?
FigureX shows the performance degradation of a single client writing updates to
a decoupled namespace and pausing to send updates to the metadata server. We
scale the namespace sync interval to show the trade-off of frequently pausing
or writing large logs of updates.  We use an idle core to log the updates and
to do the network transfer. The client only pauses to fork off a background
process, which is expensive as the address space needs to copied. The
alternative is to pause the client completely and write the update to disk but
since this implementation is limited by the speed of the disk, we choose the
memory-to-memory copy of the fork appraoch.`

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png} \caption{
[\href{https://...}{source}] Slowdown of a single client periodically syncing
updates to the gobal namespace. The crossover point represents the trade-off of
frequent updates of small journal files and infrequent updates of large journal
files.\ref{fig:slowdown-sync}.  \label{fig:slowdown-sync}} \end{figure}

% Does this implementation need to be described in the implementation?
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing updates to a decoupled namespace and pausing to send updates to
the metadata server. We scale the namespace sync interval to show the trade-off
of frequently pausing or writing large logs of updates.  We use an idle core to
log the updates and to do the network transfer. The client only pauses to fork
off a background process, which is expensive as the address space needs to
copied. The alternative is to pause the client completely and write the update
to disk but since this implementation is limited by the speed of the disk, we
choose the memory-to-memory copy of the fork appraoch.`
